---
title: "5- Manage vmr Providers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{5- Manage vmr Providers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

# The __vmr__ Providers

## Presentation

__vmr__ providers are "tools" that manage the virtual machines instances such as _VirtualBox_ (default in __vmr__), _docker_, _vmware_, _aws_, _openstack_, ...  

Actually only _VirtualBox_ is available in __vmr__ package.

## VirtualBox provider

__vmr__ can manage some of virtualbox options.  
Options available can be find here:
```{r eval=FALSE}
vb.opt <- virtualboxOptions(details = FALSE)
```

To set a name to the virtualbox machine:  
```{r eval=FALSE}
vb.opt$name <- "My Virtualbox name"
```

To disable GUI:  
```{r eval=FALSE}
vb.opt$gui <- FALSE
```

To add more cpus and memory:  
```{r eval=FALSE}
vb.opt$modifyvm$cpus <- 3
vb.opt$modifiy$memory <- 8192
```

More options can be find here [https://www.virtualbox.org/manual/ch08.html#vboxmanage-modifyvm](https://www.virtualbox.org/manual/ch08.html#vboxmanage-modifyvm)  

## Vignette summary

1. [Working with __vmr__ package](O1-workwithvmr.html)
2. [Start my first environment](O2-vmrFirstStep.html)
3. [Manage __vmr__ environment](O3-vmrManagevmr.html)
4. [Manage boxes](O4-vmrManageBoxes.html)
5. [Manage providers](O5-vmrManageProviders.html)
6. [Development with __vmr__](O6-vmrDev.html)
7. [CI/CD](O7-vmrcicd.html)
8. [Functions resume](O8-vmrResume.html)

### Next vignette : [6-Development](O6-vmrDev.html)
