---
title: "7- Use vmr for CI/CD"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{7- Use vmr for CI/CD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---

# CI/CD

You can set up a __vmr__ environment to use it in CI/CD pipelines.

Once you set up your __vmr__ environment take a snapshot of it.

```{r eval=FALSE}
vmrTakeSnapshot("cicdversionR")
```

## GitLab Runner CI/CD

Then you can get the command to run, to add it as a GitLab Runner:
```{r eval=FALSE}
virtualboxGitlabRunner(vmr_env,
                       gitlab_url = "gitlab.com",
                       gt_token = "<mytoken>",
                       snapshot_name = "cicdversionR",
                       vm_name = <VirtualBox VM Name>)
```
Copy and paste the return command in a terminal where GitLab Runner and the __vmr__ environment are installed.

## Vignette summary

1. [Working with __vmr__ package](O1-workwithvmr.html)
2. [Start my first environment](O2-vmrFirstStep.html)
3. [Manage __vmr__ environment](O3-vmrManagevmr.html)
4. [Manage boxes](O4-vmrManageBoxes.html)
5. [Manage providers](O5-vmrManageProviders.html)
6. [Development with __vmr__](O6-vmrDev.html)
7. [CI/CD](O7-vmrcicd.html)
8. [Functions resume](O8-vmrResume.html)

### Next vignette : [8- Functions resume](O8-vmrResume.html)
